Make any stupid plot you want

### 2021-01-08 draft/sections/implementation.tex
refactored vector simplex + point w/ new fiber structure

fig, ax = plt.subplots()
artist = primative_Q(E, V)
ax.add_artist(artist)
\end{minted}

@@

    def is_section(self, section):
        """checks if a section is from a given fiber bundle:
        are values in F, are keys in K"""
\end{minted}
We add a monoid field to the schema like structure of the fiber since the monoid actions are the constraints on the $\nu$ and $Q$. We implement $K$ using the triangulization scheme described in section~\ref{sec:triangulization}. This means we expect data to be provided as tables where the name encodes the connectivity:

@@

\subsubsection{Sections}
As described in section~\ref{sec:section_data}, the data values are encode as the section of the fiber bundle. We implement this as as a wrapper class around a data container object of the form:
\begin{minted}
class Section:
    FB = FiberBundle(K, F)

    def __init__(self, *args):
        pass
    def view(self, simplex="vertex"):
        """"converts data into atomic column order for get method
        # maybe also pass in the columns?
        """
        return {fieldname: data}
\end{minted}

@@

\begin{minted}{python}
class Encoder:
    def __init__(self, args):
        pass
    def validate(self, monoid):
        pass
    def convert(self, value):
        return converted_value
\end{minted}

@@

\subsection{Graphic: $\mathcal{H}$}

>>>>

fig, ax = plt.subplots()
artist = Q(E, V)
ax.add_artist(artist)
\end{minted}

@@

    def is_section(self, section):
        """checks if a section is from a given fiber bundle:
        are values in F, are keys in K"""
        pass
\end{minted}
We add a monoid field to the schema like structure of the fiber since the monoid actions are the constraints on the $\nu$ and $Q$. We implement $K$ using the triangulization scheme described in section~\ref{sec:triangulization}. This means we expect data to be provided as tables where the name encodes the connectivity:

@@

\subsubsection{Sections}
As described in section~\ref{sec:section_data}, the data values are encode as the section of the fiber bundle. We implement this as as a wrapper class around a data container object of the form:
\begin{minted}{python}
class Section:
    FB = FiberBundle(K, F)

    def __init__(self, *args):
        pass
    def view(self, simplex="vertex"):
        #convert data into atomic column order 
        return {fieldname: data}
\end{minted}

@@

\begin{minted}{python}
class Encoder:
    def __init__(self, args):
        pass
    def validate(self, monoid):
        #check if transform supports monoid action
        pass
    def convert(self, value):
        # convert value to libraries internal normalized form
        pass
\end{minted}

@@

\subsection{Graphic: $\mathcal{H}$}
We inherent from the current Matplotlib artists for our $Q$, which is responsible for constructing a curried fully specified internal representation of the graphic.
\begin{minted}{python}
class Q(BaseClass):
    required = {}
    optional = {}
    def __init__(self, data, *args, kwargs):
        # check that required and optional visual parameters are passed in
        # check that the transforms can be applied to the data 
        pass
    def draw(self, render, *args, **kwargs):
        # get frozen atomic section of the data 
        # apply  transforms data
        # set internal attributes of the graphic q generates
        #hands off to backends to draw on screen
        super().draw(renderer, *args, **kwargs)
\end{minted}
While equation~\ref{eq:artist} specifies that the values of $\mu$ can be generated before they are input to $Q$, we curry the opertaions of obtaining the data and performing the transforms to the draw method because that allows us to more easily propogate updates to the data to the screen.
